Poincar\'e--Friedrichs constants over triangulated domains

### 2024-06-22 main.tex
some improvements

We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
Given a domain $\Omega \subseteq \bbR^n$ and $1 \leq p \leq \infty$,
we search for a constant $C > 0$ such that 
\begin{align*}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
Even though the existence of such a bounded linear potential construction is not evident a priori, 
picking the average-free potential 
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
\end{align*}
is a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
\begin{align*}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align*}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.

@@

Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^n$ for the corresponding Lebesgue space of vector fields. 
We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.

@@

Whenever $T$ is an $n$-dimensional simplex 
\begin{align*}
    \kappa(T)
    := 
    \frac{ \diam(T)^n }{ n! \vol(T) }
    .
\end{align*}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align*}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align*}
Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align*}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align*}
This indicator quantifies how much reflection across the shared face distorts the goemetry.

% and $\Phi : \Delta^n \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \kappa(T)
%     := 
%     \frac{ \diam(T)^n }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\Phi : \Delta^n \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \Phi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \Phi^{-1} \|
        \leq 
        \sqrt{2n^n} 
        % \frac{ n! \vol(T) } { \diam(T)^n }
        \kappa(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^n / \det(\Jacobian\Phi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^n }{ \det(\Jacobian\Phi) } 
        \sigma_n
        \leq 
        \sqrt{2n^n} 
        \frac{ \diam(T)^n }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        &\leq 
        \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^n}{n! \vol(T_2)} 
        \leq 
        \kappa(T_1) \kappa(T_2)
        ,
        \\
        \diam(T_1)
        &\leq 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \leq 
        \kappa(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^n} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^n }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        \sqrt{2n^n} 
        \frac{ n! \vol(T_2) } {\diam(T_2)^n } 
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \diam(F)
        \sqrt{2n^n} \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        \diam(F)^{-1}
        \leq 
        \sqrt{2n^{n+1}}
        \frac{ \diam(T_1)^n }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^n } 
        .
    \end{align*}
    All the desired results thus follow. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^n}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^n}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

\begin{remark}
    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^n / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

@@

%  Since $\calT$ is strongly connected, there exists an enumersation of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

@@

We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
We recall that this means that for every $x \in \underlying{\calT}$
there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^n$
such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^n \suchthat |x| \leq 1 \}$
or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional.

@@

Recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^n$ for vector-valued functions with each component in $L^{p}(\Omega)$.

In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    W^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    W^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
More generally, ...
\\

We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $U,V \subset \mathbb{R}^3$ are open sets and suppose that $\phi: U \to V$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(V) \to L^{p}(U)$,
$\phi^{\curl}: \bfL^{p}(V) \to \bfL^{p}(U)$, 
and
$\phi^{\divergence}: \bfL^{p}(V) \to \bfL^{p}(U)$. 
and
$\phi^{\rm b}: L^{p}(V) \to L^{p}(U)$. 
They are defined by % TODO: change inverse convention from here on 
\begin{equation}\label{eq_definition_piola}
\begin{aligned}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \frac{ \Jacobian\phi^{-1} }{\det\Jacobian\phi^{-1}} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{aligned}
\end{equation}
where $v \in L^{p}(V)$ and $\bfw \in \bfL^{p}(V)$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$
These mappings are invertible. 
%
% trace properties 
%
The commutativity properties
\begin{equation}\label{eq_piola_commute}
\begin{aligned}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{aligned}
\end{equation}
for $v \in W^{p}(\grad,U)$, $\bfv \in W^{p}(\curl,U)$, and $\bfw \in W^{p}(\divergence,U)$.  
%

\subsection{Exterior Algebra}

In mathematics, Euclidean space, denoted \(\mathbb{R}^n\), is a fundamental concept representing the \(n\)-dimensional generalization of the familiar 2D and 3D spaces. Multilinear forms are scalar-valued functions that take multiple vectors as input and return a scalar and which are linear in each argument. This leads us to the study of alternating algebra, which focuses on antisymmetric multilinear forms.
Alternating algebra plays a crucial role in various areas of mathematics, including geometry and physics.
\\

Let $V$ be a real vector space. 
Given an integer $k \geq 0$, We let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
if 
\[ 
    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
    = 
    \text{sign}(\pi) 
    u( v_1, v_2, \ldots, v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.

>>>>

We take the Poincar\'e--Friedrichs inequality for the gradient of scalar functions as a conceptual point of reference.
Given a domain $\Omega \subseteq \bbR^{n}$ and $1 \leq p \leq \infty$,
we search for a constant $C > 0$ such that 
\begin{align*}
    \min\limits_{c\in\bbR}
    \| u - c \|_{L^{p}(\Omega)}
    \leq 
    C_{\grad,p} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    .
\end{align*}
Finding a potential of a given gradient $\nabla u$ is generally a nonlinear operation. 
The operator norm of any \emph{linear} potential construction is an upper bound for the Poincar\'e--Friedrichs constant. 
Even though the existence of such a bounded linear potential construction is not evident a priori, 
picking the average-free potential 
\begin{align*}
    \Phi_{\grad}( \bff ) 
    := 
    \argmin\limits_{ \substack{ v \in W^{1,p}(\Omega) \\ \int_\Omega v = 0 } } \| \nabla v - \bff \|_{L^{p}(\Omega)},
    \quad 
    \bff \in \nabla W^{1,p}(\Omega)
\end{align*}
is a linear operation. Its operator norm is the constant in the Poincar\'e inequality 
\begin{align*}
    \| u - u_{\Omega} \|_{L^{p}(\Omega)}
    \leq 
    C_{\rm P} \| \nabla u \|_{L^p(\Omega)},
    \quad 
    u \in W^{1,p}(\Omega)
    ,
\end{align*}
where $u_\Omega$ denotes the average of $u$.
Considerable research effort has gone into finding (or estimating) the optimal constants in the Poincar\'e--Friedrichs inequalities or Poincar\'e inequalities.

@@

Let us assume that $\Omega \subseteq \bbR^{n}$ is an open set. 
Given any $p \in [1,\infty]$, we let $L^p(\Omega)$ denote the Lebesgue space over $\Omega$ with integrability exponent $p$, and we write $\bfL^p(\Omega) := L^p(\Omega)^{n}$ for the corresponding Lebesgue space of vector fields. 
We also write $W^{1,p}(\Omega)$ for the first-order Sobolev space over $\Omega$ with integrability exponent $p$.

@@

Whenever $T$ is an $n$-dimensional simplex 
\begin{align*}
    \kappa(T)
    := 
    \frac{ \diam(T)^{n} }{ n! \vol(T) }
    .
\end{align*}
Moreover, when $\calT$ is an $n$-dimensional simplicial complex, we introduce 
\begin{align*}
    \kappa(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \kappa(T),
%     \qquad 
%     \delta(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \diam(T) }{ \diam(T') },
    \qquad 
    \rho(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \frac{ \vol(T) }{ \vol(T') }.
\end{align*}
Whenever $S,T$ are two $n$-simplices that are a common face $F$ of codimension $1$, we let $\Xi_{S,T} : S \rightarrow T$ denote the affine diffeomorphism 
that preserves $F$. We define 
\begin{align*}
    \xi(\calT) := \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \in \subsimplex_{n-1}(\calT) } } \| \Xi_{S,T} \|.
\end{align*}
This indicator quantifies how much reflection across the shared face distorts the geometry.

% and $\Phi : \Delta^{n} \rightarrow T$ is an affine diffeomorphism from the reference simplex,
% we define the quantity 
% \begin{align*}
%     \kappa(T)
%     := 
%     \frac{ \diam(T)^{n} }{ n! \vol(T) }
%     .
% \end{align*}

\begin{lemma}\label{lemma:affinetransform}
    Let $T$ be an $n$-simplex and let $\Phi : \Delta^{n} \rightarrow T$ be an affine diffeomorphism. Then 
    \begin{align*}
        \| \Jacobian \Phi \|
        \leq 
        \sqrt{n} \cdot \diam(T)
        ,
        \qquad 
        \| \Jacobian \Phi^{-1} \|
        \leq 
        \sqrt{2n^{n}} 
        % \frac{ n! \vol(T) } { \diam(T)^{n} }
        \kappa(T)^{-1}
        \diam(T)^{-1}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    We easily verify the first inequality. To prove the second inequality, let $\sigma_1 \geq \dots \geq \sigma_n \geq 0$ denote the singular values of $\Jacobian\Phi$ in descending order.
    Then $\sigma_1/\sigma_n \leq \sigma_1^{n} / \det(\Jacobian\Phi)$. Hence 
    \[
        \diam(T) 
        \leq 
        \sqrt{2} \sigma_1 
        \leq 
        \sqrt{2} 
        \frac{ \sigma_1^{n} }{ \det(\Jacobian\Phi) } 
        \sigma_n
        \leq 
        \sqrt{2n^{n}} 
        \frac{ \diam(T)^{n} }{ n! \vol(T) } 
        \sigma_n
        .
    \]
    The desired result is thus evident. 
\end{proof}

\begin{lemma}\label{lemma:volumecomparison}
    Let $T_1$ and $T_2$ be two $n$-simplices that share a common face $F$. Then 
    \begin{align*}
        \frac{ \vol(T_1) }{ \vol(T_2) }
        &\leq 
        \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
        \cdot 
        \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
        \leq 
        \kappa(T_1) \kappa(T_2)
        ,
        \\
        \diam(T_1)
        &\leq 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \diam(F)
        \leq 
        \kappa(T_1)
        \diam(F)
        .
    \end{align*}
    If $\Xi : T_1 \rightarrow T_2$ is an affine diffeomorphism, then 
    \begin{align*}
        \| \Jacobian \Xi \|
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        \leq 
        \sqrt{2n^{n+1}} 
        \frac{ \kappa(T_1) }{ \kappa(T_2) }
        .
    \end{align*}
\end{lemma}
\begin{proof}
    Let $h_1$ and $h_2$ be the heights of $F$ in the simplices $T_1$ and $T_2$, respectively. 
    Then $\vol(T_1) = h_1 \vol(F)/n!$ and $\vol(T_2) = h_2 \vol(F)/n!$, and thus $\vol(T_1)/\vol(T_2) = h_1/h_2$.
    We estimate 
    \begin{align*}
        h_1 &\leq \diam(T_1) \leq \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} \diam(F),
        \\
        h_2 &\geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(T_2) \geq n! \cdot \frac{\vol(T_2)}{\diam(T_2)^{n}} \diam(F)
        .
    \end{align*}
    The first estimate follows. 
    Let $h$ be the height of some face $F'$ other than $F$ in $T_1$. Then $h \leq \diam(F)$, and with similar arguments as before: 
    \begin{align*}
        \diam(F)
        \geq 
        h
        =
        n!
        \frac{ \vol(T_1) }{ \vol(F') }
        \geq 
        \frac{ n! \vol(T_1) }{ \diam(T_1)^{n} }
        \cdot 
        \diam(T_1)
        .
    \end{align*}
    That shows the second estimate. 
    Lastly, letting $\Xi : T_1 \rightarrow T_2$ be as above, we find 
    \begin{align*}
        \| \Jacobian \Xi \|
        &
        \leq 
        \sqrt{n} 
        \cdot 
        \diam(T_1)
        \sqrt{2n^{n}} 
        \frac{ n! \vol(T_2) } {\diam(T_2)^{n} } 
        \diam(T_2)^{-1}
        \\&
        \leq 
        \sqrt{n} 
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \diam(F)
        \sqrt{2n^{n}} \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        \diam(F)^{-1}
        \leq 
        \sqrt{2n^{n+1}}
        \frac{ \diam(T_1)^{n} }{ n! \vol(T_1) }
        \frac{ n! \vol(T_2) } { \diam(T_2)^{n} } 
        .
    \end{align*}
    All the desired results thus follow. 
    % Together with analogous estimates that swap the roles of $h_1$ and $h_2$, we find 
    % \begin{align*}
    %     \max\left( \frac{h_1}{h_2}, \frac{h_2}{h_1} \right)
    %     \leq 
    %     \frac{\diam(T_1)^{n}}{n! \cdot \vol(T_1)} 
    %     \cdot 
    %     \frac{\diam(T_2)^{n}}{n! \vol(T_2)} 
    %     .
    % \end{align*}
\end{proof}

\begin{remark}
    % Whenever $T$ is an $n$-dimensional simplex, the ratio $\diam(T)^{n} / \vol(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    % We can also rescale that by a factor of $1/n!$, as suggested from the above. 
    Whenever $T$ is an $n$-dimensional simplex, the ratio $\kappa(T)$ measures the ``shape quality'' of a simplex and is instance of a so-called \emph{shape measure}.
    In our convention, the reference simplex has unit shape measure.
    This geometric ratio equals what is known as \emph{fatness} in differential geometry~\cite{cheeger1984curvature} and is precisely the reciprocal of the \emph{fullness} discussed by Whitney~\cite{whitney2012geometric}. 
    The \emph{thickness} of a simplex is the ratio of its smallest height to its diameter~\cite{munkres2016elementary}.
    Alternative shape measures have been used throughout the literature of numerical analysis and computational geometry to quantify the quality of simplices.
    One example, commonly referenced in finite element literature, is the ratio of the diameter and the radius of the largest inscribed circle of a simplex 
    (see~\cite[p.61, Definition 5.1]{braess2001finite}, ~\cite[p.97, Definition (4.2.16)]{brenner2008mathematical},~\cite[Definition~11.2]{ern2021finite}). 
\end{remark}

@@

%  Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j(m) < m$ such that $F_m := T_m \cap T_{j(m)}$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

@@

We define an $n$-dimensional simplicial complex to be a \emph{manifold triangulation} if the underlying set $\underlying{\calT}$ is an $n$-dimensional manifold with boundary.
We recall that this means that for every $x \in \underlying{\calT}$
there exists $\epsilon > 0$ and an embedding $\phi : \Ball_\epsilon(x) \cap \underlying{\calT} \rightarrow \bbR^{n}$
such that $\phi(0) = 0$ and $\phi$ is an isomorphism either onto the closed unit ball $\calB = \{ x \in \bbR^{n} \suchthat |x| \leq 1 \}$
or onto $\{ x \in \calB \suchthat x_1 \geq 0 \}$.
Any simplicial complex that triangulates an $n$-dimensional manifold must be $n$-dimensional.

@@

\subsection{Review of vector calculus}

We discuss the Sobolev spaces of vector calculus and their transformation behavior. 
Let $\Omega \subseteq \bbR^{3}$ be a bounded open set. 
First, recall that $L^{p}(\Omega)$ is the space of scalar-valued $p$-integrable functions defined on $\Omega$
and that $\bfL^{p}(\Omega) := L^{p}(\Omega)^{n}$ for vector-valued functions with each component in $L^{p}(\Omega)$. 
In the three-dimensional setting, we are particularly interested in the Sobolev vector analysis. 
$W^p(\grad,\Omega) := W^{1,p}(\Omega)$ is the space of scalar-valued $L^{p}(\Omega)$ functions with weak gradients in $\bfL^{p}(\Omega)$, and we have 
\[
    W^p(\grad,\Omega) = \{ u \in L^{p}(\Omega) \suchthat \grad v \in \bfL^{p}(\Omega) \}
\]
The space $W^{p}(\curl,\Omega)$ of vector-valued $\bfL^{p}(\Omega)$ functions with weak curls in $\bfL^{p}(\Omega)$
and the space of vector-valued $\bfL^{p}(\Omega)$ functions with weak divergences in $L^{p}(\Omega)$ are defined as 
\[
    \bfW^{p}(\curl,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \curl \bfu \in \bfL^{p}(\Omega) \},
    \quad 
    \bfW^{p}(\divergence,\Omega) = \{ \bfu \in \bfL^{p}(\Omega) \suchthat \divergence \bfu \in L^{p}(\Omega) \}.
\]
We are interested in transformations of these Sobolev tensor fields from one domain onto the other. 
Suppose that $\Omega, \Omega' \subset \mathbb{R}^3$ are open sets and suppose that $\phi: \Omega \to \Omega'$ is a bi-Lipschitz mapping.
The gradient-, curl-, divergence-conforming Piola transformations are the mappings 
$\phi^{\grad}: L^{p}(\Omega') \to L^{p}(\Omega)$,
$\phi^{\curl}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$, 
$\phi^{\divergence}: \bfL^{p}(\Omega') \to \bfL^{p}(\Omega)$,
and
$\phi^{\rm b}: L^{p}(\Omega') \to L^{p}(\Omega)$. 
They are defined by 
\begin{subequations}\label{eq_definition_piola}
\begin{align}
    \phi^{\grad}(v) &= v \circ \phi, \\
    \phi^{\curl}(\bfw) &= (\Jacobian\phi^{T} \bfw) \circ \phi, \\
    \phi^{\divergence}(\bfw) &= \left( \frac{ \Jacobian\phi^{-1} }{\det\Jacobian\phi^{-1}} \bfw \right)  \circ \phi, \\
    \phi^{\rm b}(v) &= \left( \det\Jacobian\phi^{-1} v \right)  \circ \phi,
\end{align}
\end{subequations}
where $v \in L^{p}(\Omega')$ and $\bfw \in \bfL^{p}(\Omega')$, 
and where $\Jacobian\phi$ is the Jacobian matrix of $\phi$. 
These mappings are invertible. 
%
% TODO: bounds
%
We use the commutativity relations 
\begin{subequations}\label{eq_piola_commute}
\begin{align}
    \grad (\phi^{\grad} (v)) &= \phi^{\curl}(\grad v), 
    \\
    \curl (\phi^{\curl}(\bfv)) &= \phi^{\divergence}(\curl \bfv) 
    % TODO: watch the sign 
    \\
    \divergence (\phi^{\divergence}(\bfw)) &= \phi^{\rm b}(\divergence \bfw)
\end{align}
\end{subequations}
for $v \in W^{p}(\grad,\Omega)$, $\bfv \in W^{p}(\curl,\Omega)$, and $\bfw \in W^{p}(\divergence,\Omega)$.  
We summarize this as a commuting diagram:
\begin{align*}
    \begin{CD}
        W^{1,p}(\grad,\Omega') @>{\grad}>> \bfW^{p}(\curl,\Omega') @>{\curl}>> \bfW^{p}(\divergence,\Omega') @>{\divergence}>> L^{p}(\Omega')
        \\
        @VV{\phi^{\grad}}V 
        @VV{\phi^{\curl}}V 
        @VV{\phi^{\divergence}}V 
        @VV{\phi^{\rm b}}V 
        \\
        W^{1,p}(\grad,\Omega ) @>{\grad}>> \bfW^{p}(\curl,\Omega ) @>{\curl}>> \bfW^{p}(\divergence,\Omega ) @>{\divergence}>> L^{p}(\Omega )
    \end{CD}
\end{align*}

\begin{remark}
    Our notion of Piola transform along a mapping $\phi : \Omega \rightarrow \Omega'$ goes in the opposite direction of the mapping:
    scalar and vector fields over $\Omega'$ are transformed into scalar and vector fields over $\Omega'$.
    This is in accordance with the notion of pullback, that we will review shortly. 
    One advantage of that definition is that it also makes sense whenever the transformation is not a diffeomorphism. 
\end{remark}

%

%
% trace properties 
%

\subsection{Review of exterior calculus}

We also investigate this from the perspective of exterior calculus. 
We give a brief introduction into this topic. 
Let $V$ be a real vector space. 
Given an integer $k \geq 0$, We let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
if 
\[ 
    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
    = 
    \text{sign}(\pi) 
    u( v_1, v_2, \ldots, v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.
